### 2025-10-26 modern-portfolio-theory.qmd
20250903 - updates to address updated data files
20251026 - edits/additions

In terms of diversification, it can be helpful to diversify in multiple ways.
First, it can be helpful not to rely on just one or two "stud" players.
If they are on bye or have a down week, your team is more likely to suffer.
Also, there are risks in picking multiple offensive players from the same team.
If you draft your starting Quarterback and Wide Receiver from the same team (e.g., the Cowboys), you are exposing your fantasy team to considerable risk.
For instance, if you have the Quarterback and Wide Receiver from the same team, and the team has a poor offensive outing, that will have a greater impact.
You can limit your downside risk by diversifying—drafting players from different teams.
That way if the Cowboys' offense does poorly in a given week, your fantasy team will not be as affected.
Having multiple players on a juggernaut offense can be a boon, but it can be challenging to predict which offense will lead the league.

@@

We can also examine the efficient frontier of fantasy performance based on the mean and variability of players' projected week-to-week fantasy points [@Hitchings2012; archived at <https://perma.cc/JQ6G-KSRT>].

>>>>

In terms of diversification, it can be helpful to diversify in multiple ways.
First, it can be helpful not to rely on just one or two "stud" players.
If they are on bye or have a down week, your team is more likely to suffer.
Another way to diversify is to draft players with different bye weeks so you do not have multiple starting players on bye in a given week.
Also, there are risks in picking multiple offensive players from the same team.
If you draft your starting Quarterback and Wide Receiver from the same team (e.g., the Cowboys), you are exposing your fantasy team to considerable risk.
For instance, if you have the Quarterback and Wide Receiver from the same team, and the team has a poor offensive outing, that will have a greater impact.
You can limit your downside risk by diversifying—drafting players from different teams.
That way if the Cowboys' offense does poorly in a given week, your fantasy team will not be as affected.
Having multiple players on a juggernaut offense can be a boon, but it can be challenging to predict which offense will lead the league.

@@

We can also examine the efficient frontier of fantasy performance based on the mean and variability of players' historical (actual) week-to-week fantasy points [@Hitchings2012; archived at <https://perma.cc/JQ6G-KSRT>].
